SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-21 maintex.tex
defined MPL-8, removed redundant paragraph in S2.1

The MaNGA survey targets galaxies from a subset of 41,154 galaxies in the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_i}$ $<$ -24.0, where $\mathcal{M_i}$ is the rest frame $i$-band magnitude within the survey's elliptical Petrosian apertures. MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light). In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.

@@

In our previous work, \citetalias{Fu:2018}, using the 2168 unique galaxies from DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU. In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.

>>>>

The MaNGA survey targets galaxies from a subset of 41,154 galaxies in the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_i}$ $<$ -24.0, where $\mathcal{M_i}$ is the rest frame $i$-band magnitude within the survey's elliptical Petrosian apertures. MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light). In this work we use the data from the 8th MaNGA Product Launch (MPL-8), which covers 6142 unique galaxies observed by July 3, 2018.

@@
